Viability of FTIR on fossil pollen

### 2020-10-12 manuscript.Rmd
changes from Fri

The study of plant micro and macrofossil (spores, seed and pollen),recovered from lake sediments and peat bogs, is an integral part of Palaeoecology and Palaeobotany.
Pollengrains are an important tool to reconstruct past vegetational, environmental and climatic changes. 
EXAMPLES

Palaeo relies on taxonomic identification of pollen based on morphology.
Not always possible.
Recently IR spectro has emerged as a promising candidate to improve taxonomic resolution and automation of pollen counting.

Pollen is preserved in lake sediments and has shown to be resistant to diagenetic processes and found in most palaeoecological records.

FTIR used on fossil papers in the past use acetolysed pollen or other chemically extracted pollen. 
There has not been a comparison between fresh and untreated fossil pollen.
In order to compare which compounds are missing and still present in fossil pollen.

>>>>

The study of plant micro and macrofossil (spores, seed and pollen),recovered from lake sediments and peat bogs, is an integral part of Palaeoecology and Palaeobotany.
Pollengrains are resistant to the diagenetic processes that occur in the formation of sediments, bogs and other deposits, which makes pollen records 
an important tool to reconstruct past floristic, vegetational and environmental changes. 
EXAMPLES

The high preservation of pollen grains in the geological record is because of the resistant biopolymer sporopollenin, which is the main building block of the outer pollen grain wall (exine).

More and more details have been revealed about the exact structure of sporopollenin, e.g. importance of aromatic compounds, cross-linked aliphatic components [@liMolecularStructurePlant2019], similarity to lignins.

In recent years, the study of pollen grain chemistry has lead to new information important for biological and palaeoecological research.
Taxonomic differences have been identified in the chemistry of pollen, which highlight the potential of pollen identification with chemical methods in palaeoecological research.
Chemical fingerprinting of pollen has the potential of higher taxonomic resolution, automation of pollen identification and offers a more objective method than traditional morphological methods.
as well as an environmental signal stored in the chemistry of pollen (UV Proxy), which could be used as a UV-proxy.

acetolysis alters sporopollenin [@dominguezIsolationIntactPollen1998; @schulzeosthoffPhenolsIntegratedCompounds1987] affecting solubility

FTIR used on fossil papers in the past use acetolysed pollen or other chemically extracted pollen. 
There has not been a comparison between fresh and untreated fossil pollen.
In order to compare which compounds are missing and still present in fossil pollen.
chemical degradation of pollen during diagenesis or depth.
